Generative Adversarial Networks

### 2017-12-04 cs6735/project/report.tex
small updates (computer is crashing)

\begin{algorithm}[H]
  \SetAlgoLined
  \Input{$n$: The number of training iterations} \linebreak
  \Input{$k$: The number of discriminator iterations} \linebreak
  \For{training iteration in n} {
    \For{discriminator iteration in k} {
      sample $m$ vectors $\{z^{(1)},...,z^{(m)}\}$ from distribution $p_z(z)$\;
      sample $m$ vectors $\{x^{(1)},...,x^{(m)}\}$ from the training samples\;
      update the discriminator using its stochastic gradient
      $$\nabla_{\theta_d}\frac{1}{m}\sum_{i=1}^{m}[\log(D(x^{(i)}))+\log(1-D(G(z^{(i)})))]$$
    }
    sample $m$ vectors $\{z^{(1)},...,z^{(m)}\}$ from distribution $p_z(z)$\;
    update the generator using its stochastic gradient\;
    $$\nabla_{\theta_g}\frac{1}{m}\sum_{i=1}^{m}[\log(1-D(G(z^{(i)})))]$$
  }
  \caption{The initial generative adversarial network algorithm developed by Goodfellow \textit{et al.} in 2014 \citep{2014arXiv1406.2661G}. Multiple variations of this algorithm have since been produced. One of the benefits of adversarial networks is that they may be updated using back propagation.}
\end{algorithm}

\section{Issues}
There exist several issues that characterize generative adversarial networks. Some are related design of GANs or their underlying network implementations. These issues lay at the forefront of GAN research.

\subsection{Instability} \label{sec:instability}
Generative adversarial networks are often characterized by their instability \citep{2017arXiv170100160G}. The training process makes use of gradient descent which does not guarantee convergence to the Nash equilibrium, the game theory equilibrium that involves two competing players. This training process for GANs is different than network optimization which is common in discriminative models. When either the generator or discriminator trains, even if that specific network improves, the other may regress. This sometimes leads to the scenario where each network repeatedly undo's the other's progress. This problem is not specific to GANs, but to any zero-sum game situations \citep{2017arXiv170100160G}.

@@

\subsection{Evaluation}
The evaluation procedure for generative adversarial networks remains an open debate as there exist no clear quantitative measurement to evaluate the models \citep{2017arXiv170100160G}. For example, models with high likelihood may produce unrealistic samples and models with low likelihood may produce realistic samples \citep{2017arXiv170100160G}. Several variations of the GANs examine the tradeoffs of divergence measures other than the original Kullback-Leibler divergence \citep{2015arXiv151101844T}. It has been shown that different metrics lead to different tradeoffs and different evaluations favor different models \citep{2015arXiv151101844T}. Therefore, it is important to asses one's model within the context of the whole application \citep{2015arXiv151101844T}.

@@

\section{Architecture Variations}
Research within the field of deep generative modeling has increased exponentially since the debut of generative adversarial networks in 2014. Significant improvements are being made with respect to image quality and training stability. Hundreds of papers have been released since 2014 (see figure \ref{fig:CumulativeNumberofGANPapersbyMonth}) which propose numerous architectural variations.

\begin{figure}
\centering
\includegraphics[scale=0.43]{cumulative_gans}
\caption{The cumulative amount of papers written about generative adversarial networks. The graph shows the exponential growth of GANs within the past three years. Image maintained by Avinash Hindipur \citep{November2017GANZoo}.}
\label{fig:CumulativeNumberofGANPapersbyMonth}
\end{figure}

\subsection{Fully Connected GANs}
The first generative adversarial network paper by Goodfellow \textit{et al.} made use of relatively simple fully connected neural networks for the generator and discriminator models \citep{2017arXiv171007035C}. These are networks where each neuron in one layer is connected to every neuron in the following layer. This design is able to generate simple images and useful for proof of concept; however, several other architectures have overtaken this implementation \citep{2017arXiv171007035C}.

>>>>

\begin{algorithm}[H]
  \SetAlgoLined
  \Input{$n$: The number of training iterations} \linebreak
  \Input{$k$: The number of discriminator iterations} \linebreak
  \For{training iteration in n} {
    \For{discriminator iteration in k} {
      sample $m$ vectors $\{z^{(1)},...,z^{(m)}\}$ from distribution $p_z(z)$\;
      sample $m$ vectors $\{x^{(1)},...,x^{(m)}\}$ from the training samples\;
      update the discriminator using its stochastic gradient
      $$\nabla_{\theta_d}\frac{1}{m}\sum_{i=1}^{m}[\log(D(x^{(i)}))+\log(1-D(G(z^{(i)})))]$$
    }
    sample $m$ vectors $\{z^{(1)},...,z^{(m)}\}$ from distribution $p_z(z)$\;
    update the generator using its stochastic gradient\;
    $$\nabla_{\theta_g}\frac{1}{m}\sum_{i=1}^{m}[\log(1-D(G(z^{(i)})))]$$
  }
  \caption{The initial generative adversarial network algorithm developed by Goodfellow \textit{et al.} in 2014 \citep{2014arXiv1406.2661G}. Multiple variations of this algorithm have since been produced. One of the benefits of adversarial networks is that they are able to make use of back propagation for training.}
\end{algorithm}

\section{Issues}
There exist several issues that characterize GANs. Some are due to the architecture of GANs while others to implementations of the generator and descriminator. These issues lay at the forefront of GAN research.

\subsection{Instability} \label{sec:instability}
GANs are often characterized by their instability \citep{2017arXiv170100160G}. The training process makes use of gradient descent which does not guarantee convergence to the Nash equilibrium, the game theory equilibrium that involves two competing players. This training process for GANs is different than network optimization which is common in discriminative models. When either the generator or discriminator trains, even if that specific network improves, the other may regress. This sometimes leads to the scenario where each network repeatedly undo's the other's progress. This problem is not specific to GANs, but to any zero-sum game situations \citep{2017arXiv170100160G}.

@@

\subsection{Evaluation}
The evaluation procedure for GANs remains an open debate as there exist no clear quantitative measurement to evaluate the models \citep{2017arXiv170100160G}. For example, models with high likelihood may produce unrealistic samples and models with low likelihood may produce realistic samples \citep{2017arXiv170100160G}. Several variations of the GANs examine the tradeoffs of divergence measures other than the original Kullback-Leibler divergence \citep{2015arXiv151101844T}. It has been shown that different metrics lead to different tradeoffs and different evaluations favor different models \citep{2015arXiv151101844T}. Therefore, it is important to asses one's model within the context of the whole application \citep{2015arXiv151101844T}.

@@

\section{Architecture Variations}
Research within the field of deep generative modeling has increased exponentially since the debut of GANs in 2014. Significant improvements are being made with respect to image quality and training stability. Hundreds of papers have been released since 2014 (see figure \ref{fig:CumulativeNumberofGANPapersbyMonth}) which propose numerous architectural variations.

\begin{figure}
\centering
\includegraphics[scale=0.43]{cumulative_gans}
\caption{The cumulative amount of papers written about generative adversarial networks by month. The graph shows the exponential growth of GANs within the past three years. Image maintained by Avinash Hindipur \citep{November2017GANZoo}.}
\label{fig:CumulativeNumberofGANPapersbyMonth}
\end{figure}

\subsection{Fully Connected GANs}
The first GAN paper by Goodfellow \textit{et al.} made use of relatively simple fully connected neural networks for the generator and discriminator models \citep{2017arXiv171007035C}. These are networks where each neuron in one layer is connected to every neuron in the following layer. This design is able to generate simple images and useful for proof of concept; however, several other architectures have overtaken this implementation \citep{2017arXiv171007035C}.
